\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}

\title{Bibliography}
\author{Gaurav Shajepal, Annya Kar}
\date{\today}
\usepackage{hyperref}
\begin{document}

\maketitle
 
%\section{First section}
 
Japan is an island country in East Asia. Japan has thousands of years of history which have been shaping their culture until today. Combining traditions and modern technology is one of the uniquenesses of Japan. Manners and customs are an important part of many facets of Japanese life. Japanese people grow up picking up the subtleties of this unique culture as they go through life, respecting the invisible and varied societal rules. Japanese people appear at first glance to be one of the most socially and ethnically homogenous groups in the world. Dive into the diverse cuisine from sushi to ramen, from soba to tempura – a whole variety of unfamiliar delicious foods to try. 
Japan has over 700 universities to choose from and 10 of them are ranked in the top 200 worldwide. That already shows their extraordinary academic dedication. Japan has the second highest number of Nobel prize winners of all countries in the world. In a nutshell, the quality of teaching is very high and important to the Japanese.
Because of your experience of having studied in Japan, the doors will be wide open on the job market! In Japan, big companies want to recruit more international graduates to represent their global businesses.
 
\medskip

\begin{thebibliography}{9}
\bibitem{Mext} 
\href{http://www.mext.go.jp/en/index.html.}{“MEXT : Ministry of Education, Culture, Sports, Science and Technology.”} Mext.Go.Jp, 1 Jan. 2016

  
\bibitem{Topglobal} 
\href{https://tgu.mext.go.jp/en/index.html.}{“Top Global University Project.”} Mext.Go.Jp, 1 Jan. 2019

 
\bibitem{Globalization}
\href{https://www.nippon.com/en/in-depth/a02801/}{“Globalization and Higher Education Reforms in Japan: The Obstacles to Greater International Competitiveness.”} Nippon.Com, 21 Jan. 2019


\bibitem{japanguide}
\href{https://www.studyjapan.go.jp/en/.}{“Study In Japan Comprehensive Guide.”} 1 Jan. 2017


\bibitem{phd}
\href{https://www.findaphd.com/study-abroad/asia/phd-study-in-japan.aspx.}{“PhD Study in Japan - A Guide for Postgraduate Students. Www.FindAPhD.Com”} www.FindAPhD.com, 1 Jan. 2000

\bibitem{foreginersinjapan}
\href{https://www.findaphd.com/study-abroad/asia/phd-study-in-japan.aspx.}{“Foreigners in Japan: Student Stories.”} Times Higher Education (THE), 16 Feb 2017


\bibitem{Language}
\href{www.iwillteachyoualanguage.com/learn/japanese/japanese-tips/japanese-culture-for-foreigners.}{“Insider Secrets You Need To Know.”}I Will Teach You A Language, 7 Feb. 2019


\bibitem{Greece}
\href{www.commisceo-global.com/resources/country-guides/japan-guide.}{“Home.” Greece - Language, Culture and Doing Business Etiquette}


\bibitem{Udemy}
\href{blog.udemy.com/japanese-culture-facts/.}{“Japanese Culture Facts: 23 Things You May Not Have Known.”} Udemy Blog

  
\bibitem{Education japan}
\href{www.japantimes.co.jp/community/2017/01/25/issues/education-japan-2016-new-solutions-age-old-problems-teaching-english-bullying/#.XGbF2TNKhPY.}{“Education in Japan in 2016: New Solutions and Age-Old Problems, from Teaching English to Bullying.”} The Japan Times


\bibitem{nihon}
\href{gogonihon.com/en/blog/learn-about-the-japanese-education-system/}{“Learn about the Japanese Education System and What Makes It Unique.”} Go! Go! Nihon, 11 July 2018


\bibitem{NCEE}
\href{ncee.org/what-we-do/center-on-international-education-benchmarking/top-performing-countries/japan-overview/.}{“Japan Overview.” } NCEE 


\bibitem{School}
\href{www.tokyo-icc.jp/guide_eng/educ/01.html.}{"Japanese School System | Tokyo International Communication Committee"}

\bibitem{Nomadic}
\href{nomadicboys.com/8-fun-interesting-facts-about-japan/.}{“Our 8 Fun, Quirky and Interesting Facts about Japan.”}Nomadic Boys, 8 Feb. 2019

\bibitem{Nomadic}
\href{listverse.com/2017/01/09/10-crazy-historic-facts-about-japan/.}{“10 Crazy Historic Facts About Japan.”}Listverse, Listverse, 21 Oct. 2018

\bibitem{Nomadic}
\href{www.seriousfacts.com/japan-facts/.}{“40 Interesting Facts about Japan.”}Serious Facts, 7 Aug. 2018

 






\end{thebibliography}
 
\end{document}